Large Scale Structure Reconstruction with Short-Wavelength Modes

### 2019-10-24 paper/v2.tex
1

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{simplewick}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{color}
\usepackage{enumitem}
\usepackage[linktocpage=true]{hyperref} 
\hypersetup{
    colorlinks=true,       
    linkcolor=red,         
    citecolor=blue,        
    filecolor=magenta,      
    urlcolor=blue           
}
\usepackage[all]{hypcap} 
\definecolor{darkgreen}{cmyk}{0.85,0.1,1.00,0} 
\definecolor{darkorange}{rgb}{1.0,0.2,0.0}
\newcommand{\scott}[1]{{\color{darkgreen} #1}}
\newcommand{\peikai}[1]{{\color{blue} #1}}
\newcommand{\prvs}[1]{{\color{magenta} #1}}
\newcommand{\AL}[1]{{\color{magenta} AL: #1}}
\newcommand{\MR}[1]{{\color{blue} MR: #1}}
\newcommand{\RC}[1]{{\color{darkorange} #1}}
\newcommand{\nl}{\\ \indent}
\begin{document}
\title{Large Scale Structure Reconstruction with Short-Wavelength Modes}
\author{\large Peikai Li}
\affiliation{Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
\author{\large Scott Dodelson}
\affiliation{Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
\author{\large Rupert A. C. Croft}
\affiliation{Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
\affiliation{McWilliams Center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15213, USA}

@@

\end{abstract}
\maketitle
\noindent {\it Introduction.}
Measuring the distribution of matter on large scales is one of the goals of cosmological surveys. The information contained on large scales may provide information about issues ranging from the turnover in the power spectrum (and therefore the total matter density) to the accelerated universe to anomalies observed in the cosmic microwave background to primordial nongaussianity. Direct measurements are difficult because of observational systematic effects, so indirect approaches have been considered. Small scale structure grows differently in the presence of an large-scale overdensity: it is as if the mean background density is larger than on average. This relation between long- and short-wavelength modes has been discussed in recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}. The method of using the small scale position-dependent power spectrum to compute the squeezed-limit bispectrum also indicates that small scale perturbations can be used to infer large scale information \cite{Chiang:2014pos}\cite{Chiang:2015poss}. In order to fully achieve this goal, here we construct a quadratic estimator to measure long-wavelength modes indirectly.

Standard perturbation theory (SPT) \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop} identifies the second-order perturbation of a short-wavelength mode as a convolution of a short- and a long-wavelength mode. Abstractly, this is similar to
cosmic microwave background (CMB) lensing~\cite{Hu:2002mr}, where the CMB temperature field has a second-order correction due to the gravitational field along line of sight. Similarly in our case the short-wavelength mode's nonlinear terms are related to its large scale environment.
The construction of a CMB lensing quadratic estimator makes use of the fact that small scale two-point correlations of CMB temperature modes have off-diagonal terms due to large scale perturbations caused by gravitational lensing. The same statistical feature shows up in our case as well -- the off-diagonal terms of the small scale correlations are no longer zero, due to the effect of large scale modes. Thus we can create a quadratic estimator for long-wavelength modes using exactly the same formalism.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{simplewick}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{color}
\usepackage{enumitem}
\usepackage[linktocpage=true]{hyperref} 
\hypersetup{
    colorlinks=true,       
    linkcolor=red,         
    citecolor=blue,        
    filecolor=magenta,      
    urlcolor=blue           
}
\usepackage[all]{hypcap} 
\definecolor{darkgreen}{cmyk}{0.85,0.1,1.00,0} 
\definecolor{darkorange}{rgb}{1.0,0.2,0.0}
\newcommand{\scott}[1]{{\color{darkgreen} #1}}
\newcommand{\peikai}[1]{{\color{blue} #1}}
\newcommand{\prvs}[1]{{\color{magenta} #1}}
\newcommand{\AL}[1]{{\color{magenta} AL: #1}}
\newcommand{\MR}[1]{{\color{blue} MR: #1}}
\newcommand{\RC}[1]{{\color{darkorange} #1}}
\newcommand{\nl}{\\ \indent}
\begin{document}
\title{Large Scale Structure Reconstruction with Short-Wavelength Modes}
\author{\large Peikai Li}
\affiliation{Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
\affiliation{McWilliams Center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
\author{\large Scott Dodelson}
\affiliation{Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
\affiliation{McWilliams Center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
\author{\large Rupert A. C. Croft}
\affiliation{Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
\affiliation{McWilliams Center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15213, USA}

@@

\end{abstract}
\maketitle
\noindent {\it Introduction.}
Measuring the distribution of matter on large scales is one of the goals of cosmological surveys. The information contained on large scales may provide information about issues ranging from the turnover in the power spectrum (and therefore the total matter density) to the accelerated universe to anomalies observed in the cosmic microwave background to primordial nongaussianity. Direct measurements are difficult because of observational systematic effects, so indirect approaches have been considered. Small scale structure grows differently in the presence of an large-scale overdensity: it is as if the mean background density is larger than on average. This relation between long- and short-wavelength modes has been discussed in recent years \cite{Baldauf:2011fer}\cite{Li:2014ssc}\cite{Barreira:2017res}. The method of using the small scale position-dependent power spectrum to compute the squeezed-limit bispectrum also indicates that small scale perturbations can be used to infer large scale information \cite{Chiang:2014pos}\cite{Chiang:2015poss}. In order to fully achieve this goal, here we construct a quadratic estimator to measure long-wavelength modes indirectly.

Standard perturbation theory (SPT) \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop} identifies the second-order perturbation of a short-wavelength mode as a convolution of a short- and a long-wavelength mode. Abstractly, this is similar to
cosmic microwave background (CMB) lensing~\cite{Hu:2001dt}\cite{Hu:2002mr}, where the CMB temperature field has a second-order correction due to the gravitational field along line of sight. Similarly in our case the short-wavelength mode's nonlinear terms are related to its large scale environment.
The construction of a CMB lensing quadratic estimator makes use of the fact that small scale two-point correlations of CMB temperature modes have off-diagonal terms due to large scale perturbations caused by gravitational lensing. The same statistical feature shows up in our case as well -- the off-diagonal terms of the small scale correlations are no longer zero, due to the effect of large scale modes. Thus we can create a quadratic estimator for long-wavelength modes using exactly the same formalism.
